---
title: "Customer Data Analysis"
output: html_notebook
---

We want to analyze our customer data, and better understand them.  Please identify:

```{r setup}
library(dplyr, magrittr)
load('exerciseData.rda')
```

A quick test of viewing the data
```{r}
head(arrange(dataset_emails,desc(role)),n=10)
```

* The top 10 countries by active enterprise users
```{r}
country_tenants <- left_join(dataset_relation, dataset_emails, by='email_id') %>%
    left_join(., dataset_tenants, by='tenant_id') %>%
    filter(active_enterprise_users_last_30d > 0) %>%
    group_by(country) %>%
    summarise(total_enterprise_users = sum(active_enterprise_users_last_30d))
head(arrange(country_tenants,desc(total_enterprise_users)),n=11)
```
```{r}

```
* The top 10 operating systems by open and total tickets
```{r}

```
* The distribution of pageviews per group
```{r}

```
* The distribution differences on pageviews per login method
```{r}

```
* What differences do you find between developers and non-developers?
```{r}

```
* What are the most and least used technologies in tenants?
```{r}

```
* Please mark any inconsistencies you find in the data that you'd research further if you were working at Auth0
```{r}

```
* Create at least 3 visualizations using R which you consider interesting for the provided data
```{r}

```
