---
title: "Customer Data Analysis"
output: html_notebook
---

We want to analyze our customer data, and better understand them.  Please identify:

```{r setup}
library(dplyr, magrittr)
load('exerciseData.rda')
```

A quick test of viewing the data
```{r}
head(arrange(dataset_emails,desc(role)),n=10)
```

* The top 10 countries by active enterprise users
```{r}
#many to many
#dataset_emails$country
#dataset_tenants$active_enterprise_users_last_30d

# includes duplicate counts
# country_tenants <- left_join(dataset_relation, dataset_emails, by='email_id') %>%
#     left_join(., dataset_tenants, by='tenant_id') %>%
#     filter(active_enterprise_users_last_30d > 0) %>%
#     group_by(country) %>%
#     summarise(total_enterprise_users = sum(active_enterprise_users_last_30d))
# head(arrange(country_tenants,desc(total_enterprise_users)),n=11)

non_zero <- filter(dataset_tenants, active_enterprise_users_last_30d > 0)
country_tenants <- left_join(dataset_relation, non_zero, by='tenant_id') %>%
    left_join(., dataset_emails, by='email_id') %>%
    select(tenant_id, country, active_enterprise_users_last_30d) #%>%
country_tenants <- unique(country_tenants) # doesn't remove all duplicates
arrange(country_tenants,desc(active_enterprise_users_last_30d))
```
* The top 10 operating systems by open and total tickets
```{r}
#many to many
#dataset_emails$sperating_system
#dataset_tenants$account_total_tickets
#dataset_tenants$account_open_tickets
```
* The distribution of pageviews per group
```{r}
#one to many
#dataset_emails$source_group
#dataset_pageviews$visits
```
* The distribution differences on pageviews per login method
```{r}
#one to many
#dataset_emails$login_method
#dataset_pageviews$visits
```
* What differences do you find between developers and non-developers?
```{r}
#dataset_emails$role
```
* What are the most and least used technologies in tenants?
```{r}
#dataset_tenants$technologies_used
```
* Please mark any inconsistencies you find in the data that you'd research further if you were working at Auth0
```{r}

```
* Create at least 3 visualizations using R which you consider interesting for the provided data
```{r}

```
